Estimating Trending Topics on Twitter with Small Subsets of the Total Data

### 2015-01-12 521_project_paper.tex
added outline

@@

data structures

algorithms
clean up algorithm section
- make sure changes in implementation are reflected in algorithm

>>>>

to note: our goal was to make a real time query algorithm that USES
the history (in condensed form) to help understand current time 
we're remembering the past with less accuracy to save space (realistic model)
in order to get good estimates of present trending

this means we are not trying to query the past the way Hokusai is.

@@

data structures
description
-- fib heap
-- queue
-- frequency hash table
-- History (own subsection)

algorithms
description
- make sure changes in implementation are reflected in algorithm 
-- querying the (History)
-- updating the data structure
------ adding to the data structure
----------- frequency hash table update/ heap update / (update history every time block - mention why we can add, etc, some of the theory from the Hokusai paper)
------ removing from the data structure (our snapshot of the present)
----------- every time unit of the present, we remove outdated frequencies
-- top k hashtags (real time)

runtime analysis
space analysis
accuracy analysis

design choices for data structure
-- data structure modification (History vs Hokusai)
-- fibonacci heap 
-- heap key function
